Higher-Order unification for free!

### 2024-04-17 paper/main.tex
remove snippet

If instead we want \Uo{} to follow the second strategy and pick an
arbitrary solution we can modify \progress by applying the desired heuristic.
For instance, in $X \appsep a \appsep b = Y \appsep b$, the last
argument of the two terms is the same and unification can succeed by assigning
$X a$ to $Y$. This heuristic can be implemented by adding the following rule:

\input{code/progress_heuristic}
%\noindent
%Note that \elpiIn{UV} is in \llambda as well as \elpiIn{T}. 
\vspace{-1em}
\section{Actual implementation in Elpi}\label{sec:implementation}

>>>>

If instead we want \Uo{} to follow the second strategy and pick an
arbitrary solution we can modify \progress by applying the desired heuristic
instead of failing.
For instance, in $X \appsep a \appsep b = Y \appsep b$, the last
argument of the two terms is the same and unification can succeed by assigning
$X a$ to $Y$. This heuristic is used by~\cite{sozeau08}.

%\input{code/progress_heuristic}
%\noindent
%Note that \elpiIn{UV} is in \llambda as well as \elpiIn{T}. 
\vspace{-1em}
\section{Actual implementation in Elpi}\label{sec:implementation}
